Gradual Soundness: Lessons from Static Python

### 2022-01-28 pj-7.1/paper.tex
ack
pj: more acks, more author

\author[a]{Kuang-Chen Lu}
\authorinfo{(\email{LuKuangchen1024@gmail.com}) } %% { is a PhD student at Brown University.}
\affiliation[a]{Brown University, Providence, RI, USA}
\author[a]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) } %% {is a PLT member and a postdoc at Brown University.}
\author[b]{Carl Meyer}
\authorinfo{(\email{carljm@fb.com}) } %% FILL
\affiliation[b]{Meta, Menlo Park, CA, USA}
\author[b]{Dino Viehland}
\authorinfo{(\email{dinoviehland@fb.com}) } %% FILL
\author[a]{Shriram Krishnamurthi}
\authorinfo{(\email{shriram@brown.edu}) } %% {is the Vice President of Programming Languages (no, not really) at Brown University.}

@@

\acks{
  \SP{} was developed by Sinan Cepel, William Meehan, Carl Meyer, Aniket Panse,
  and Dino Viehland.
  The Brown authors contributed to the language by modeling it independently; they
  are not part of the \SP{} team.

  Special thanks to Guido van Rossum for helping the authors meet via Twitter
  and for his ongoing contributions to Python.
  This work was partly supported by the US National Science Foundation.
  Greenman acknowledges support from NSF grant 2030859 to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
}

>>>>

\author[a]{Kuang-Chen Lu}
\authorinfo{(\email{LuKuangchen1024@gmail.com}) } %% { is a PhD student at Brown University.}
\affiliation[a]{Brown University, Providence, RI, USA}
\author[a]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) } %% {is a PLT member and a postdoc at Brown University.}
\author[b]{Carl Meyer}
\authorinfo{(\email{carljm@fb.com}) } %% FILL
\affiliation[b]{Meta, Menlo Park, CA, USA}
\author[b]{Aniket Panse}
\authorinfo{(\email{aniketpanse@fb.com}) } %% FILL
\author[b]{Dino Viehland}
\authorinfo{(\email{dinoviehland@fb.com}) } %% FILL
\author[a]{Shriram Krishnamurthi}
\authorinfo{(\email{shriram@brown.edu}) } %% {is the Vice President of Programming Languages (no, not really) at Brown University.}

@@

\acks{
  \SP{} and the Cinder JIT were developed by
  Max Bernstein,
  John Biesnecker,
  Jacob Bower,
  Sinan Cepel,
  Tiansi Hu,
  Orvid King,
  Vladimir Matveev,
  William Meehan,
  Carl Meyer,
  Matt Page,
  Aniket Panse,
  Brett Simmers,
  Andrei Talaba,
  Dino Viehland,
  and Shiyu Wang.
  The Brown authors contributed to the language by modeling it independently; they
  are not part of the \SP{} team.

  Special thanks to Twitter, thanks to which the two teams
  (specifically, Meyer and Krishnamurthi) met.
  This work was partly supported by the US National Science Foundation.
  Greenman acknowledges support from NSF grant 2030859 to the CRA for the \href{https://cifellows2020.org}{CIFellows} project.
}
